{ \fontfamily{ptm}\selectfont A big title }

### 2024-11-28 Latex Templates/Scientific 2/main.tex
>w<, changes

\author{
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{alto@mail.ubc.ca}.}~ Author Name 1
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Xianfu Wang
}

@@

\section{Section}
    Beck's book \cite{beck_first-order_2017}. 
\section{Section}

\begin{abstract} 
    \noindent
    Abstract abstract abstract.

\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Non-convex Optimizations, Proximal Point.

>>>>

\author{
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{alto@mail.ubc.ca}.}~Author Name 1
    \thanks{Department of Mathematics, I.K. Barber Faculty of Science,
    The University of British Columbia, Kelowna, BC Canada V1V 1V7. 
    E-mail:  \texttt{shawn.wang@ubc.ca}.}~ and~Author Name 2
}

@@

\begin{abstract} 
    \noindent
    Abstract abstract abstract. 
\end{abstract}
% \noindent{\bfseries 2010 Mathematics Subject Classification:}
% Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
% \noindent{\bfseries Keywords: } Non-convex Optimizations, Proximal Point.

\tableofcontents

\section{Introduction}

\section{Notations}
    Beck's book \cite{beck_first-order_2017}. 
\subsection{Foundamentals in convex analysis}
\subsection{Canonical forms of Nesterov's accelerated methods}
\section{Unifying variants of Nesterov's accelerated methods}
\section{Generic convergence anlaysis of accelerated methods}
\section{Catalyst accelerations and future works}
\section{Performence estimation problems}
\section{Methods of inexact proximal point}
\section{Nestrov's acceleration in the non-convex case}
